---
title: "Yuan Wang BST 260 HW0"
author: "Yuan Wang"
format: html
editor: visual
execute: 
  echo: false
---

First, we assign values to a, b, and c accordingly with a=1, b=3, c=2.

```{r}
#Assigning values
a <- 1
b <- 3
c <- 2
```

Then we solve the equation with the quadratic formula and print out the two solutions x_1 and x_2.

```{r}
#Quadratic formula for solution
x_1 = (-b + sqrt(b^2 - 4 * a * c)) / (2 * a)
x_2 = (-b - sqrt(b^2 - 4 * a * c)) / (2 * a)

result <- x_1 == x_2

if (any(is.nan(x_1))||any(is.nan(x_2))) {
  print("The equation has no real-number solution.")
}else if (result) {
  print ("The equation has only one solution.")
}else {
  print(paste("The two solutions to the given equation are",x_1, "and", x_2))
}
```

Then we plot the function with a certain range of x (*I use (-10,10)*). It is also desirable to zoom in with ylim() to observe the number of solutions (*I use (-20,20)*). We add a horizontal line to see the intersections with x-axis (i.e. the solutions).

```{r}
#Plot it
x <- seq(-10, 10, length=300)
plot(x, a*x^2+b*x+c, type="l", ylim = c(-20,20))
abline(h = 0, lty = 2)
```

The graph's intersections with the x-axis reveal the number of solutions to the equation.

-   If two intersections: Two solutions 

-   If one intersection: Only one solution

-   If no intersection: No real-number solution